Reliable feature point matching

### 2013-08-14 text/main/ch6_applications.tex
Added a few references to applications

\section{Panorama Recognition and Alignment}
One of the oldest practical problems approached in computer vision is 
the automatic stitching of several source images into a bigger image, 
such as panoramas and composite satellite photos\footnote{A brief 
overview of the history of image stitching can be found in Szeliski's 
book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
As part of the process of stitching together images, the individual 
images must be aligned and often transformed in perspective. Earlier 
methods relied on minimizing pixel dissimilarities in overlapping images 
while more recent methods have used local feature points to estimate the 
correct image alignment. Using local feature points carry the additional 
advantage that it is feasible to automatically recognize where each 
source image belong in the final panorama.

@@

To demonstrate the usefulness of \emph{MMC} applied to panorama 
recognition and alignment we construct a simple panorama stitcher taking
as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
and returns as output a panoramic image stitched together from the 
source images. Based on the matches found by applying \emph{MMC} to $I$, 
the images are combined in an order corresponding to how many matches 
connect them, as done by Brown and Lowe \cite{brown2007automatic}.

Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
provides a way to globally optimize the accuracy of the image alignment} 
and a lot of image enhancements such as exposure adjustment and edge 
blurring to provide a seamless panorama. While these additions improve 
the end product, they don't influence the performance of panorama 
alignment and recognition and haven't been included in the simple 
comparison algorithm.

Figure~\ref{fig:pano_example} shows an example where the added accuracy 
of MMC enables us to correctly recognitize and align source images that 
fail to be combined by Autostitch, a program using the algorithm 
proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
case the matching algorithm used in Autostitch fails to find sufficient 
matches between two images pairs to correctly position them and 
consequently doesn't produce a panorama containing all images as a 
result.

@@

\section{Near Duplicate Detection}
If we look at two images, we can often easily tell if one image 
resembles the other enough to be redundant in a photo album. In computer 
vision this task becomes a lot less trivial because our idea of a 
duplicate image might only require there being some object or scene in 
common between the image pair. In addition the object or scene might 
have been taken from a different angle and under different camera 
settings. Facing these challenges, a lot of work has been done trying to 
reliably recognize duplicates both with regards to corporate 
intellectual property as well as consumer photo albums because both 
applications provide useful tools.  A company might be interested in 
finding images that are derived from their intellectual property, while 
consumers taking vacation photos might be interested in grouping 
duplicate images to allow for easier photo organization.

@@

The \emph{PhotoCluster} method introduced by Vonikakis et al.  
\cite{vas2013cluster} shows the best clustering performance on the 
California-nd dataset \cite{jinda2012california} which contains a set of
annotated vacation images similar to a typical photo album in a consumer
product. \emph{PhotoCluster} works by grouping images in several steps 
using first image meta data and global features to obtain a set of 
proposed clusters. Then local features are used to find the best 
matching images in these proposed clusters yielding the final groups of 
near duplicate images. To show the viability of \emph{MMC} in the 
application of near duplicated detection, we modify the PhotoCluster 
method to use \emph{MMC} for matching images instead of \emph{Ratio} 
which was previously used. Due to the time consumption of \emph{MMC}, 
all images where resized to to 10\% before being compared. Outside of 
that, the experiments were performed exactly as documented in 
\cite{vas2013cluster}.

\begin{table}[htb]
\caption{Results from Near Duplicate Detection at 10\% scale}
\label{table:ndd}
	\centering
%	\small
\begin{tabular}{r*{2}{r}}
\hline
    Method: & Ratio & MMC   \\
	\noalign{\smallskip}
	%
    F1 score: & 0.4654 & 0.5459 \\
	\hline
\end{tabular}
\end{table}

The results of the comparison can be seen in Table~\ref{table:ndd}. It 
shows that \emph{MMC} improves performance by 8.05\% over the original 
framework using \emph{Ratio} to match images. For comparison, the 
performance improvement of \emph{PhotoCluster} compared to XMatch 
\cite{zhao2009scale}, the second best performing algorithm on the 
California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.

>>>>

\section{Panorama Recognition and Alignment}
One of the oldest practical problems approached in computer vision is 
the automatic stitching of several source images into a bigger image, 
such as panoramas and composite satellite photos\footnote{A brief 
overview of the history of image stitching can be found in Szeliski's 
book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
As part of the process of stitching together images, the individual 
images must be aligned and often transformed in perspective. Earlier 
methods relied on minimizing pixel dissimilarities in overlapping images
(\cite{shum1997panoramic}, \cite{szeliski1995direct}) while more recent 
methods have used local feature points to estimate the correct image 
alignment (\cite{mclauchlan2002image}, \cite{capel1998automated}, 
\cite{brown2007automatic}).  Using local feature points carry the 
additional advantage that it is feasible to automatically recognize 
where each source image belong in the final panorama.

@@

To demonstrate the usefulness of \emph{MMC} applied to panorama 
recognition and alignment we construct a simple panorama stitcher taking
as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
and returns as output a panoramic image stitched together from the 
source images. Based on the matches found by applying \emph{MMC} to $I$, 
the images are combined in an order corresponding to how many matches 
connect them, as done by Brown and Lowe \cite{brown2007automatic}. That 
is, homographies are estimated between all images with sufficient 
feature point matches in between them as returned by \emph{MMC}. Then 
the images are stitched together starting with the image pair having the 
highest amount of matches, and continuing in a decrease order of 
matches.

Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
provides a way to globally optimize the accuracy of the image alignment} 
and various image enhancements such as exposure adjustment and edge 
blurring to provide a seamless panorama. While these additions improve 
the end product, they don't influence the performance of the alignment 
and recognition parts of panorama stitching and for this reason haven't 
been included in the simple comparison algorithm.

Figure~\ref{fig:pano_example} shows an example where the added accuracy 
of MMC enables us to correctly recognize and align source images that 
fail to be combined by Autostitch, a program using the algorithm 
proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
case the matching algorithm used in Autostitch fails to find sufficient 
matches between two images pairs to correctly position them and 
consequently doesn't produce a panorama containing all images as a 
result.

@@

\section{Near Duplicate Detection}
If we look at two images, we can often easily tell if one image 
resembles the other enough to be redundant in a photo album. In computer 
vision this task is nontrivial because our idea of a duplicate image 
might only require there being some object or scene in common between 
the image pair. In addition the object or scene might have been taken 
from a different angle and under different camera settings. Facing these 
challenges, work has been done trying to reliably recognize duplicates 
both with regards to corporate intellectual property as well as consumer 
photo albums.  A company might be interested in finding images that are 
derived from their intellectual property, while it allows consumers 
taking vacation photos to automatically grouping duplicate images which 
allows for easier photo organization.

@@

The \emph{PhotoCluster} method introduced by Vonikakis et al.  
\cite{vas2013cluster} shows the best clustering performance on the 
California-nd dataset \cite{jinda2012california} which contains a set of
annotated vacation images similar to a typical photo album in a consumer
product. \emph{PhotoCluster} works by grouping images in several steps 
using first image meta data and global features to obtain a set of 
proposed clusters. Then local features are used to find the best 
matching images in these proposed clusters yielding the final groups of 
near duplicate images. To show the viability of \emph{MM} and \emph{MMC} 
in the application of near duplicated detection, we modify the 
PhotoCluster method to use the proposed algorithms for matching images 
instead of \emph{Ratio} which was previously used. The experiments were 
performed as documented in \cite{vas2013cluster}, however due to the 
running time of \emph{MMC} it is intractable to calculate the test 
scores on full scale images. To showcase the performance of \emph{MMC} 
we add a test case using images resizes to 10\% of their original size.

\begin{table}[htb]
\caption{Results from Near Duplicate Detection}
\label{table:ndd}
	\centering
%	\small
\begin{tabular}{r*{3}{r}}
\hline
F1 score & \emph{Ratio} & \emph{MM} & \emph{MMC}   \\
	\noalign{\smallskip}
	%
    10\% Scale: & 0.5013 & 0.5990 & 0.5785 \\
    100\% Scale: & 0.0 & 0.0 & --- \\
	\hline
\end{tabular}
\end{table}

The results of the comparison can be seen in Table~\ref{table:ndd}. It 
shows that \emph{MM} improves performance by 19.49\% over the original 
framework using \emph{Ratio} to match images. For comparison 
\emph{PhotoCluster} improves on the results of Xmatch 
\cite{zhao2009scale}, the second best performing algorithm on the 
California-nd dataset according to \cite{vas2013cluster}, with 2.52\%.
